Grammar-Based Concept Alignment for Domain-Specific Machine Translation

### 2021-05-16 paper/paper.tex
fixed typos found by C.

% importance of lexica in DSMT
However, lexical exactness is, in this context, just as important as grammaticality. 
An important part of the design of a Controlled Natural Language (CNL) is the creation of a high-quality translation lexicon, preserves both semantics and grammatical correctness.

% how it is done right now and issues
A translation lexicon is often built manually, which is a time consuming task requiring significant linguistic knowledge. 
When the task is based on a corpus of parallel example sentences, it is possible to automate part of this process by means of statistical word and phrase alignment techniques \cite{brown-etal-1993-mathematics, och-ney-2000-improved, dyer-etal-2013-simple}. 
None of them is, however, suitable for the common case in which only a small amount of example data is available --- typically, which just one occurrence of each relevant lexical item.

>>>>

% importance of lexica in DSMT
However, lexical exactness is, in this context, just as important as grammaticality. 
An important part of the design of a Controlled Natural Language (CNL) is the creation of a high-quality translation lexicon, preserving both semantics and grammatical correctness.

% how it is done right now and issues
A translation lexicon is often built manually, which is a time consuming task requiring significant linguistic knowledge. 
When the task is based on a corpus of parallel example sentences, it is possible to automate part of this process by means of statistical word and phrase alignment techniques \cite{brown-etal-1993-mathematics, och-ney-2000-improved, dyer-etal-2013-simple}. 
None of them is, however, suitable for the common case in which only a small amount of example data is available --- typically, with just one occurrence of each relevant lexical item.
